\theseminartitle \\ \small \thetitle

### 2021-09-29 tex/paper.tex
Finished paper content

In the broadest sense, benchmarks can be divided into competitive and non-competitive benchmarks. The main motivation of competitive benchmarks is hereby the development of standardized quality criteria that can be used to compare different systems. Certain sources also emphasize this importance on the competitiveness by providing a more detailed definition of the term benchmark, i.e. "a standard tool for competitive evaluation and comparison of competitive systems" (\cite{kistowski2015} p. X).

@@

Regardless of the competitiveness, or lack thereof, of a benchmark the key metrics that are evaluated are often similar or even identical. While historically the main metrics of importance were e.g. security, system reliability and energy efficiency, modern benchmarks also try to cover much more aspects of a software. We will discuss a selection of the quality attributes listed by Kounev et al. that are usually target of modern benchmarks(\cite{Kounev} p. 6 f):

\paragraph{Performance} The term Performance itself can be interpreted in many different means. For this paper, we will focus on one of the most basic interpretations: The amount of work done compared to the time and resources used. A much more in-depth explanation of different performance measures is given by Kounev et al. (See \cite{Kounev} p. 49 ff)

\paragraph{Scalability} TODO Definition needed

\paragraph{Energy Efficiency} TODO Definition needed

\paragraph{Reliability} TODO Definition needed

When it comes to benchmarking strategies two approaches are most prominent: Fixed-Time and Fixed-Work benchmarks. A Fixed-Work Benchmark here describes the most intuitive approach for benchmarking: We fix a specified amount of work $W_i$ and measure the required time $T_i$ that is required to fulfil this work.

While Fixed-Work benchmarks are easy to understand and implement, it introduces an implicit performance bottleneck that is also known as \textit{Amdahl's Law}. It states that the maximum possible performance improvement that can be achieved in Fixed-Work Benchmarks is upper-bounded by the fraction of work that is performed by the component that is being improved (See \cite{Kounev} p. 9f).

In Fixed-Time benchmarks, instead of fixing the amount of work $W_i$, the time $T_i$ is bound and the amount of work finished in this time is measured as a metric. As opposed to Fixed-Work Benchmarks the Fixed-Time Benchmarks do not suffer the issue of an upper-bounded maximum improvement as for every improvement, the reduced time can be used to process further work units (See \cite{Kounev} p. 11).

Additionally there are also further approaches that does not employ fixed time or work at all, but rather employ variable-time and -work characteristics. For this case the metric is a function of the time $T$ and the work $W$. While this technique provides maximum flexibility, this approach is not suitable for all types of benchmarks (See \cite{Kounev} p. 12)

@@

Over the years, researchers and industry associates alike have defined several criteria that are considered desirable by modern standards. Often the exact terminology of these criteria differs based on authors and the specific application domain, however the concepts in general are similar. Kounev at al. list five core criteria that will be defined in a little more detail in this chapter (\cite{Kounev} p. 13f). A much more in depth discussion of these criteria was performed by Kistowski et al. (See \cite{kistowski2015})

\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application. This is what the "Relevance" of a benchmark refers to. It tries to define how relevant the produced information is to a potential user of a software. According to Kistowski et al. this makes it "perhaps the most important characteristic" (\cite{kistowski2015} p. 334). However the relevance of a benchmark may also limits the benchmarks applicability meaning, that a highly relevant benchmark for a specific system or component might only narrow applicability while benchmarks with a broad applicability will have a lower relevance but for a wider selection of applications. Kistowski et al. further elaborate on this with specific examples (\cite{kistowski2015} p. 334f)

\paragraph{Reproducibility} Reproducibility ensures that it is possible for a third party to produce ideally the same results for a given test environment. Reproducibility covers both the consistency between multiple runs on the same system as well as creating the same results on another environment with a semantically equivalent configuration.

However, with modern hard- and software systems, optimal reproducibility has become challenging. For both hard- and software there are several factors that induce variability. From a hardware side things such as the physical disc layout or network connections may affect benchmarking results. For software systems the causes for variability stem from various different sources. from a low-level perspective, things such as thread scheduling can influence the benchmark results. From a higher level perspective a benchmark has to consider the configurability of a software system itself. Modern software systems often offer lots of different configuration options which can be used to create a tailor made system-variant. En- or disabling a specific feature might heavily influence the performance of a benchmark.

According to Huppler, an ideal benchmark result should be definable as a function of a hard- and software configuration (See \cite{huppler2009} p. 335). However for real-world applications, modelling such a function is far too complex which requires the benchmark designer to try to model reproducibility in other ways. In the end the reproducibility of a benchmark is heavily dependent on the ability to reproduce the benchmarking environment that was used to create this specific benchmark.

\paragraph{Fairness} TODO: Short explanation
\paragraph{Verifiability} TODO: Short explanation
\paragraph{Usability} TODO: Short explanation

@@

	Both of these challenges are heavily influenced by the length of software release cycles and the resulting amount of commits throughout one cycle. As an example one can take a look at a few open-source repositories. The C++ test framework \textit{googletest}\footnote{See \url{https://github.com/google/googletest}} by Google with it's most recent release (\textit{1.11.0}) in June 2021, while the last release before that (\textit{1.10.0}) was released in October 2019. During this period of 28 months roughly 700 commits have been added to the repository. Similarly for the C implementation of the \texttt{lz4} compression algorithm that can be found on GitHub\footnote{\url{https://github.com/lz4/lz4}} in the 15 months between the two most recent releases about 250 commits have been added to the code.

@@

TODO: Elaborate how/if this can be used to compare arbitrary results

@@

	Within this paper the readily available python package implemented by engineers of MongoDB will be used\footnote{TODO: Link to GitHub}. A broad overview of the algorithm that includes the exact calculation of $\hat{Q}$ is described by the work of Daly et al. (\cite{daly2020} p. 69) while an in depth description of the algorithm is given in the original paper by Matteson and James (\cite{Matteson2014}).

@@

	The main idea of the experiment that was created was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper. More specifically, we want to evaluate the following questions:
	\begin{itemize}
		\item When do we need to benchmark software?
			\begin{itemize}
				\item Is it sufficient to benchmark releases?
				\item Do we need to benchmark every commit?
			\end{itemize}
		\item How do different continuous benchmarking approaches compare with respect to:
			\begin{itemize}
				\item Complexity of implementation?
				\item Reliably detecting performance changes?
				\item Reducing the amount of manual work required by the developer?
				\item Can we use this metric to compare arbitrary commits? TODO: Maybe remove
			\end{itemize}
	\end{itemize}

@@

	To perform the experiment as described in \autoref{ssec:exp_goals} the open-source implementation \texttt{lz4}\footnote{\url{https://github.com/lz4/lz4}} will be used. \texttt{lz4} is a compression library with an active commit history. In total \texttt{lz4} offers 31 releases and more than 2500 commits in total\footnote{As of 16.09.2021}.

	For the benchmark itself the open source project \texttt{lzbench}\footnote{\url{https://github.com/inikep/lzbench}} will be used. Lzbench is an in-memory compression benchmarking tool that is designed to compare different implementations of compression algorithms. For this experiment all other compression algorithm implementations will be disabled so that only \texttt{lz4} will be benchmarked at different releases and commits.

@@

	Lzbench also offers a variety of command line switches that influence the behaviour of the benchmark. An overview of the switches that were used for executing this experiment can be found in \autoref{tab:cmd_switches}\footnote{Also see: \url{https://github.com/inikep/lzbench}}.

	\begin{table}
		\caption{Overview of used command line switches for lzbench}
		\label{tab:cmd_switches}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			\textbf{Switch} & \textbf{Description}\\
			\hline\hline
			\texttt{-elz4} & Limits the lzbench run to only benchmark the lz4 compression implementation \\
			\hline
			\texttt{-i100,100} & Sets the minimum number of compression and decompression iterations to $100$ \\
			\hline
			\texttt{-p3} & Sets the output to print the median speed of all iterations \\
			\hline
			\texttt{-j} & Join files in memory but compress them independently \\
			\hline
			\texttt{-r} & Operate recursively on directories \\
			\hline 
			\texttt{-o4} & Sets the output text format to CSV \\
			\hline
			\texttt{-v} & Disables progress information \\
			\hline
		\end{tabular}
	\end{table}

	As a workload for the compression benchmark the Silesia Data Corpus will be used\footnote{\url{http://sun.aei.polsl.pl/~sdeor/index.php?page=silesia}}. The Silesia Corpus is a diverse dataset that has specifically been designed as a compression workload with the motivation in mind to include a variety of different data sources. By this the Silesia Corpus tries to not favour any compression algorithms that perform very well on a certain type of data(TODO: Citation needed).

@@

	The benchmark was implemented using a few simple bash scripts that perform an lzbench run on a given list of commits. The benchmark script copies all source files required for building lzbench to a separate build directory. It then checks out the given commit of lz4 and overwrites the lz4 specific files in the lzbench directory. This custom built lzbench version is then used to run the benchmark. All code that was used to perform this benchmark can be found on GitHub (\cite{TODO}).

@@

	As described in the previous section the benchmark was first performed on all versioned releases in the Git repository. The results of this initial run are shown in \autoref{fig:release-bench}. It can be observed that throughout the release history the compression speed stayed relatively consistent. For the decompression speed however, multiple performance increases can be observed throughout the release history. \autoref{tab:rel-speedup} shows the relative speedup between the individual versions.

	\begin{table}
		\caption{Relative speedup between lz4 releases}
		\label{tab:rel-speedup}
	\end{table}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.8\textwidth]{graph/lz4_commits_decompression}
	\caption{Decompression speed of \texttt{lz4} between releases \textit{v1.8.1} and \textit{v1.8.2}}
	\label{fig:lz4_commit_bench}
\end{figure}

@@

\begin{figure}[ht!]
	\centering
	\includegraphics[width=0.8\textwidth]{graph/lz4hc_commits_compression}
	\caption{Decompression speed of \texttt{lz4hc} between releases \textit{v1.8.0} and \textit{v1.8.1}}
	\label{fig:lz4hc_commit_bench}
\end{figure}

@@

\begin{table}
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\textbf{Benchmark}&\textbf{Jump Detection}&\textbf{Trend Detection}&\textbf{E-Divisive Means}
		\\\hline\hline
		\texttt{lz4}&24&27&4
		\\\hline
		\texttt{lz4hc}&23&43&3
		\\\hline
	\end{tabular}
	\caption{Overview of changes detected by the different methods}
\end{table}

\begin{table}
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\textbf{Benchmark}&\textbf{Jump Detection}&\textbf{Trend Detection}&\textbf{E-Divisive Means}
		\\\hline\hline
		\texttt{lz4}&24&27&4
		\\\hline
		\texttt{lz4hc}&23&43&3
		\\\hline
	\end{tabular}
	\caption{Overview of changes detected by the different methods}
\end{table}
After applying these techniques we observed that they differ vastly in the amount of supposed performance changes that they detect. In \autoref{tab:perf_changes} we list how many performance changes were detected for each technique, while \autoref{fig:perf_commit_cp} shows a visual representation of the change points in the datasets.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4_commit_e-divisive}
		\caption{\texttt{lz4} using E-Divisive Means}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4_commit_jump}
		\caption{\texttt{lz4} using Jump Detection}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4_commit_trend}
		\caption{\texttt{lz4} using Trend Detection}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4hc_commit_e-divisive}
		\caption{\texttt{lz4hc} using E-Divisive Means}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4hc_commit_jump}
		\caption{\texttt{lz4hc} using Jump Detection}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4hc_commit_trend}
		\caption{\texttt{lz4hc} using Trend Detection}
	\end{subfigure}
	\caption{Graphical representation of all change detections on the both datasets}
	\label{fig:}
\end{figure}

@@

\begin{table}
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\textbf{Dataset}&\textbf{Change Point Commit\#}&\textbf{First detected at Commit \#}&\textbf{$\Delta$}
		\\\hline\hline
		\texttt{lz4}&3&7&4
		\\\hline
		\texttt{lz4}&52&64&12
		\\\hline
		\texttt{lz4}&251&287&31
		\\\hline
		\texttt{lz4}&313&316&6
		\\\hline
		\texttt{lz4hc}&36&37&1
		\\\hline
		\texttt{lz4hc}&104&122&18
		\\\hline
		\texttt{lz4hc}&122&123&1
		\\\hline
	\end{tabular}
	\caption{Overview of changes detected by the different methods}
\end{table}

@@

\paragraph{Reproducibility} -- As all code artifact that have been used to perform this benchmark have been documented in a GitHub repository. A third-party could use these in addition to the information given in this paper regrding the hardware configuration to closely reproduce the results.

\paragraph{Fairness} -- As for fairness there are a few things to critisize. Our benchmark is completely created artificially and is overly simplistic by nature. Therefore the fairness of our benchmarking approach could be questionable.

\paragraph{Verifiability} -- In terms of verifiability, our benchmark ensures that only a predefined software configuration is used. However our benchmark only copies the build files from an existing directory on the users hardware and does not validade if any unexpected changes have been made. In an extended approach we would rather consider the code to be cloned directly from a public Git repository, preferably with a specific commit defined.

Additionally our detailled experiment contained some outliers that we could not explain based on our findings. We now believe that this might be an error in our benchmarking approach as firstly, the achieved performance results are closely to those from recent \texttt{lz4} versions. Additionally when repeating the benchmark on a smaller subset, we could not reliably reproduce these results. Unfortunately in the timeframe of this seminar we could not identify the exact cause of this.

@@

	Secondly we believe that for future works the focus of the research question should shift a bit. While this work shows that in an optimal scenario one should benchmark every commit, this is not applicable in practive. Therefore the focus should rather shift to find strategies to preemptively select the "correct" commits for benchmarking.

	Lastly we believe that that aspect of configurability needs to be further considered. While we already collected data for two variants of \texttt{lz4}, we did not use it yet to find any collaborations between the data. We believe that exploring possibilities to link performance changes across variants can be very benefitial.

@@

Several similar work has been published regarding continuous performance benchmarking. Both Antz et al. and Waller at al. describe methods how benchmarking can be included into a continuous integration pipeline to enable continuous benchmarking(\cite{}). Additionally Daly desribes in multiple works how a continuous benchmarking approach has been introduced to MongoDB to enable better detection of performance changes.

In the domain of identifying performance changes across different software configurations and variants, Apel et al. present a novel change point detection algorithm that can identify configuration-dependent performance changes while only exploring a small subset of the configuration space (\cite{}).

Multiple works have also been presented to predict performance changes in software based in order to reduce the amount of commits that need to be benchmarked. One of these approaches is \textit{Perphecy} presented by Oliveria et al. (\cite{}). Similarly, Chen et al. present an approach which identifies which predicts which test cases may suffer from performance regressions after a code change(\cite{}).

@@

In this paper we tried to answer the question whether one should benchmark software only before releases or after every commit. We have explored both possibilities and compared different performance change detection methods. We come to the conclusion that, in an optimal scenario, benchmarking every commit would be the preferrable option.

>>>>

In the broadest sense, benchmarks can be divided into competitive and non-competitive benchmarks. The main motivation of competitive benchmarks is hereby the development of standardized quality criteria that can be used to compare different systems. Certain sources also emphasize this importance on the competitiveness by providing a more detailed definition of the term benchmark, i.e. "a standard tool for competitive evaluation and comparison of competitive systems" (\cite{kistowski2015} p. 333).

@@

Regardless of the competitiveness, or lack thereof, of a benchmark the key metrics that are evaluated are often similar or even identical. While historically the main metrics of importance were e.g. security, system reliability and energy efficiency, modern benchmarks also try to cover much more aspects of a software. According to Kounev et al. quality metrics of modern benchmarks are usually(\cite{Kounev} p. 6 f):
\begin{itemize}
	\item Performance
	\item Scalability
	\item	Energy Efficiency
	\item Reliability
\end{itemize}

%\paragraph{Performance} The term Performance itself can be interpreted in many different means. For this paper, we will focus on one of the most basic interpretations: The amount of work done compared to the time and resources used. A much more in-depth explanation of different performance measures is given by Kounev et al. (See \cite{Kounev} p. 49 ff)

%\paragraph{Scalability} TODO Definition needed

%\paragraph{Energy Efficiency} TODO Definition needed

%\paragraph{Reliability} TODO Definition needed

In terms of benchmarking strategies three general approaches can be distinguished:
\begin{enumerate}
	\item Fixed-Time Benchmarks
	\item Fixed-Work Benchmarks
	\item Variable Time- and Work-Benchmarks
\end{enumerate}

All of these offer there own benefits, drawbacks and specific use-cases. These are discussed in detail by Kounev et al.(\cite{Kounev} p. 9ff)

%When it comes to benchmarking strategies two approaches are most prominent: Fixed-Time and Fixed-Work benchmarks. A Fixed-Work Benchmark here describes the most intuitive approach for benchmarking: We fix a specified amount of work $W_i$ and measure the required time $T_i$ that is required to fulfil this work.

%While Fixed-Work benchmarks are easy to understand and implement, it introduces an implicit performance bottleneck that is also known as \textit{Amdahl's Law}. It states that the maximum possible performance improvement that can be achieved in Fixed-Work Benchmarks is upper-bounded by the fraction of work that is performed by the component that is being improved (See \cite{Kounev} p. 9f).

%In Fixed-Time benchmarks, instead of fixing the amount of work $W_i$, the time $T_i$ is bound and the amount of work finished in this time is measured as a metric. As opposed to Fixed-Work Benchmarks the Fixed-Time Benchmarks do not suffer the issue of an upper-bounded maximum improvement as for every improvement, the reduced time can be used to process further work units (See \cite{Kounev} p. 11).

%Additionally there are also further approaches that does not employ fixed time or work at all, but rather employ variable-time and -work characteristics. For this case the metric is a function of the time $T$ and the work $W$. While this technique provides maximum flexibility, this approach is not suitable for all types of benchmarks (See \cite{Kounev} p. 12)

@@

Over the years, researchers and industry associates alike have defined several criteria that are considered desirable by modern standards. Often the exact terminology of these criteria differs based on authors and the specific application domain, however the concepts in general are similar. Kounev at al. list five core criteria that are generally of interest(\cite{Kounev} p. 13f). A much more in depth discussion of these criteria was performed by Kistowski et al. (See \cite{kistowski2015})
\begin{itemize}
	\item Relevance
	\item Reproducibility
	\item Fairness
	\item Verifiability
	\item Usability
\end{itemize}
%\paragraph{Relevance} For a benchmark to be meaningful it is important that it, at least to a certain extent, reproduces some scenarios with real world application. This is what the "Relevance" of a benchmark refers to. It tries to define how relevant the produced information is to a potential user of a software. According to Kistowski et al. this makes it "perhaps the most important characteristic" (\cite{kistowski2015} p. 334). However the relevance of a benchmark may also limits the benchmarks applicability meaning, that a highly relevant benchmark for a specific system or component might only narrow applicability while benchmarks with a broad applicability will have a lower relevance but for a wider selection of applications. Kistowski et al. further elaborate on this with specific examples (\cite{kistowski2015} p. 334f)

%\paragraph{Reproducibility} Reproducibility ensures that it is possible for a third party to produce ideally the same results for a given test environment. Reproducibility covers both the consistency between multiple runs on the same system as well as creating the same results on another environment with a semantically equivalent configuration.

%However, with modern hard- and software systems, optimal reproducibility has become challenging. For both hard- and software there are several factors that induce variability. From a hardware side things such as the physical disc layout or network connections may affect benchmarking results. For software systems the causes for variability stem from various different sources. from a low-level perspective, things such as thread scheduling can influence the benchmark results. From a higher level perspective a benchmark has to consider the configurability of a software system itself. Modern software systems often offer lots of different configuration options which can be used to create a tailor made system-variant. En- or disabling a specific feature might heavily influence the performance of a benchmark.

%According to Huppler, an ideal benchmark result should be definable as a function of a hard- and software configuration (See \cite{huppler2009} p. 335). However for real-world applications, modelling such a function is far too complex which requires the benchmark designer to try to model reproducibility in other ways. In the end the reproducibility of a benchmark is heavily dependent on the ability to reproduce the benchmarking environment that was used to create this specific benchmark.

%\paragraph{Fairness} TODO: Short explanation
%\paragraph{Verifiability} TODO: Short explanation
%\paragraph{Usability} TODO: Short explanation

@@

	Both of these challenges are heavily influenced by the length of software release cycles and the resulting amount of commits throughout one cycle. As an example one can take a look at a few open-source repositories. The C++ test framework \textit{googletest} (\cite{gtest}) by Google with it's most recent release (\textit{1.11.0}) in June 2021, while the last release before that (\textit{1.10.0}) was released in October 2019. During this period of 28 months roughly 700 commits have been added to the repository. Similarly for the C implementation of the \texttt{lz4} compression algorithm that can be found on GitHub (\cite{gitlz4}) in the 15 months between the two most recent releases about 250 commits have been added to the code.

@@

@@

	Within this paper the readily available python package implemented by engineers of MongoDB will be used(\cite{gitmongo}). A broad overview of the algorithm that includes the exact calculation of $\hat{Q}$ is described by the work of Daly et al. (\cite{daly2020} p. 69) while an in depth description of the algorithm is given in the original paper by Matteson and James (\cite{Matteson2013}).

@@

	The main idea of the experiment that was created was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper. More specifically, we want to evaluate the following questions:
	\begin{itemize}
		\item When do we need to benchmark software?
			\begin{itemize}
				\item Is it sufficient to benchmark releases?
				\item Do we need to benchmark every commit?
			\end{itemize}
		\item How do different continuous benchmarking approaches compare with respect to:
			\begin{itemize}
				\item Complexity of implementation?
				\item Reliably detecting performance changes?
				\item Reducing the amount of manual work required by the developer?
			\end{itemize}
	\end{itemize}

@@

	To perform the experiment as described in \autoref{ssec:exp_goals} the open-source implementation \texttt{lz4}(\cite{gitlz4}) will be used. \texttt{lz4} is a compression library with an active commit history. In total \texttt{lz4} offers 31 releases and more than 2500 commits in total\footnote{As of 16.09.2021}.

	For the benchmark itself the open source project \texttt{lzbench}(\cite{gitlzbench}) will be used. Lzbench is an in-memory compression benchmarking tool that is designed to compare different implementations of compression algorithms. For this experiment all other compression algorithm implementations will be disabled so that only \texttt{lz4} will be benchmarked at different releases and commits.

@@

	Lzbench also offers a variety of command line switches that influence the behaviour of the benchmark. An overview of the switches that were used for executing this experiment can be found in \autoref{tab:cmd_switches}.

	\begin{table}
		\caption{Overview of used command line switches for lzbench (\cite{gitlzbench})}
		\label{tab:cmd_switches}
		\centering
		\begin{tabular}{|c|c|}
			\hline
			\textbf{Switch} & \textbf{Description}\\
			\hline\hline
			\texttt{-elz4} & Limits the lzbench run to only benchmark the lz4 compression implementation \\
			\hline
			\texttt{-i100,100} & Sets the minimum number of compression and decompression iterations to $100$ \\
			\hline
			\texttt{-p3} & Sets the output to print the median speed of all iterations \\
			\hline
			\texttt{-j} & Join files in memory but compress them independently \\
			\hline
			\texttt{-r} & Operate recursively on directories \\
			\hline 
			\texttt{-o4} & Sets the output text format to CSV \\
			\hline
			\texttt{-v} & Disables progress information \\
			\hline
		\end{tabular}
	\end{table}

	As a workload for the compression benchmark the Silesia Data Corpus will be used. The Silesia Corpus is a diverse dataset that has specifically been designed as a compression workload with the motivation in mind to include a variety of different data sources. By this the Silesia Corpus tries to not favour any compression algorithms that perform very well on a certain type of data(\cite{silesia}).

@@

	The benchmark was implemented using a few simple bash scripts that perform an lzbench run on a given list of commits. The benchmark script copies all source files required for building lzbench to a separate build directory. It then checks out the given commit of lz4 and overwrites the lz4 specific files in the lzbench directory. This custom built lzbench version is then used to run the benchmark. All code that was used to perform this benchmark can be found on GitHub (\cite{gitSysBench}).

@@

	As described in the previous section the benchmark was first performed on all versioned releases in the Git repository. The results of this initial run are shown in \autoref{fig:release-bench}. It can be observed that throughout the release history the compression speed stayed relatively consistent. For the decompression speed however, multiple performance increases can be observed throughout the release history.

@@

\begin{figure}[ht!]
	\centering
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4_commits_decompression}
		\caption{Decompression speed of \texttt{lz4}}
		\label{fig:lz4_commit_bench}
	\end{subfigure}
	\begin{subfigure}[b]{0.45\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4hc_commits_compression}
		\caption{Decompression speed of \texttt{lz4hc}}
		\label{fig:lz4hc_commit_bench}
	\end{subfigure}
	\caption{Benchmark results for individual commits}
\end{figure}

@@

@@

\begin{table}
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\textbf{Benchmark}&\textbf{Jump Detection}&\textbf{Trend Detection}&\textbf{E-Divisive Means}
		\\\hline\hline
		\texttt{lz4}&24&27&4
		\\\hline
		\texttt{lz4hc}&23&43&3
		\\\hline
	\end{tabular}
	\caption{Overview of changes detected by the different methods}
	\label{tab:perf_changes}
\end{table}
After applying these techniques we observed that they differ vastly in the amount of supposed performance changes that they detect. In \autoref{tab:perf_changes} we list how many performance changes were detected for each technique, while \autoref{fig:perf_commit_cp} shows a visual representation of the change points in the datasets.

\begin{figure}[ht!]
	\centering
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4_commit_e-divisive}
		\caption{\texttt{lz4} using E-Divisive Means}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4_commit_jump}
		\caption{\texttt{lz4} using Jump Detection}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4_commit_trend}
		\caption{\texttt{lz4} using Trend Detection}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4hc_commit_e-divisive}
		\caption{\texttt{lz4hc} using E-Divisive Means}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4hc_commit_jump}
		\caption{\texttt{lz4hc} using Jump Detection}
	\end{subfigure}
	\begin{subfigure}[b]{0.3\textwidth}
		\includegraphics[width=\textwidth]{graph/lz4hc_commit_trend}
		\caption{\texttt{lz4hc} using Trend Detection}
	\end{subfigure}
	\caption{Graphical representation of all change detections on the both datasets}
	\label{fig:perf_commit_cp}
\end{figure}

@@

\begin{table}
	\centering
	\begin{tabular}{|c||c|c|c|}
		\hline
		\textbf{Dataset}&\textbf{Change Point Commit\#}&\textbf{First detected at Commit \#}&\textbf{$\Delta$}
		\\\hline\hline
		\texttt{lz4}&3&7&4
		\\\hline
		\texttt{lz4}&52&64&12
		\\\hline
		\texttt{lz4}&251&287&31
		\\\hline
		\texttt{lz4}&313&316&6
		\\\hline
		\texttt{lz4hc}&36&37&1
		\\\hline
		\texttt{lz4hc}&104&122&18
		\\\hline
		\texttt{lz4hc}&122&123&1
		\\\hline
	\end{tabular}
	\caption{Overview of changes detected by the different methods}
	\label{tab:ediv_occ}
\end{table}

@@

\paragraph{Reproducibility} -- As all code artifact that have been used to perform this benchmark have been documented in a GitHub repository. A third-party could use these in addition to the information given in this paper regarding the hardware configuration to closely reproduce the results.

\paragraph{Fairness} -- As for fairness there are a few things to criticise. Our benchmark is completely created artificially and is overly simplistic by nature. Therefore the fairness of our benchmarking approach could be questionable.

\paragraph{Verifiability} -- In terms of verifiability, our benchmark ensures that only a predefined software configuration is used. However our benchmark only copies the build files from an existing directory on the users hardware and does not validate if any unexpected changes have been made. In an extended approach we would rather consider the code to be cloned directly from a public Git repository, preferably with a specific commit defined.

Additionally our detailed experiment contained some outliers that we could not explain based on our findings. We now believe that this might be an error in our benchmarking approach as firstly, the achieved performance results are closely to those from recent \texttt{lz4} versions. Additionally when repeating the benchmark on a smaller subset, we could not reliably reproduce these results. Unfortunately in the time frame of this seminar we could not identify the exact cause of this.

@@

	Secondly we believe that for future works the focus of the research question should shift a bit. While this work shows that in an optimal scenario one should benchmark every commit, this is not applicable in practice. Therefore the focus should rather shift to find strategies to preemptively select the "correct" commits for benchmarking.

	Lastly we believe that that aspect of configurability needs to be further considered. While we already collected data for two variants of \texttt{lz4}, we did not use it yet to find any collaborations between the data. We believe that exploring possibilities to link performance changes across variants can be very beneficial.

@@

Several similar work has been published regarding continuous performance benchmarking. Both Antz et al. and Waller at al. describe methods how benchmarking can be included into a continuous integration pipeline to enable continuous benchmarking(\cite{antz2019}, \cite{waller2015}). Additionally Daly describes in multiple works how a continuous benchmarking approach has been introduced to MongoDB to enable better detection of performance changes(\cite{daly2020}, \cite{daly2021}).

In the domain of identifying performance changes across different software configurations and variants, Apel et al. present a novel change point detection algorithm that can identify configuration-dependent performance changes while only exploring a small subset of the configuration space (\cite{apel2020}).

Multiple works have also been presented to predict performance changes in software based in order to reduce the amount of commits that need to be benchmarked. One of these approaches is \textit{Perphecy} presented by Oliveria et al. (\cite{oliveira2017}). Similarly, Chen et al. present an approach which identifies which predicts which test cases may suffer from performance regressions after a code change(\cite{chen2020}).

@@

In this paper we tried to answer the question whether one should benchmark software only before releases or after every commit. We have explored both possibilities and compared different performance change detection methods. We come to the conclusion that, in an optimal scenario, benchmarking every commit would be the preferable option.
